Arterial pulsations cannot drive intramural periarterial drainage: Significance for \Ab drainage

### 2017-07-29 paper.tex
modified introduction for reviewer 2

Alzheimer's disease (AD) is the commonest form of dementia. Although it has been studied for over 100 years \cite{Selkoe2001}, to date there is no cure as the processes relevant to its onset and progression have not yet been fully understood. The pathology of AD comprises the degeneration and death of neurons, synapse loss, neuroinflammation and the intracellular as well as extracellular accumulation of proteins \cite{Koffie2011}. The protein amyloid-\textbeta\xspace (\Ab) is produced as part of the normal metabolism of healthy brains, but it plays a major role in the development of AD \cite{Haass1992}. Its accumulation in the walls of cerebral blood vessels as cerebral amyloid angiopathy (CAA) is closely associated with the onset and progression of AD. CAA strongly correlates with the progression of AD and the degree of dementia as it appears in \SIrange{90}{96}{\percent} of AD patients \cite{Weller2006, Weller2009}.

In order to process metabolites, the brain requires a lymphatic system that transports waste products to the lymph nodes, where they are decomposed. While the rest of the body possesses a dedicated network of lymphatic vessels these do not exist in the brain \cite{Weller2010}. There is ample evidence that the basement membranes (BM) in the walls of cerebral arteries provide the clearance pathway for interstitial fluid (ISF) towards the surface of the brain, also referred to as intramural periarterial drainage (IPAD) \cite{Weller2010,Carare2008,Hawkes2011,Morris2014}. It is important not to confuse the IPAD pathway with the Virchow-Robin spaces, which are often referred to as perivascular (or ``paravascular'') spaces, possibly artefactual, located between the glia limitans and the arterial wall. Virchow-Robin spaces are virtual spaces and have no role in \Ab drainage. The BM forming the IPAD does not actually constitute a space, but rather a fluid-filled protein matrix. Our understanding of the mechanism that drives perivascular drainage through the BM is still very limited. The evidence indicates that ISF enters the BM at the capillary level and flows towards the lymph nodes in the neck via the BM cerebral arteries. This suggests that the counterintuitive phenomenon of ISF flow occurs in the reverse direction to blood flow \cite{Carare2008}.

>>>>

Alzheimer's disease (AD) is the commonest form of dementia. Although it has been studied for over 100 years \cite{Selkoe2001}, to date there is no cure as the processes relevant to its onset and progression have not yet been fully understood. The pathology of AD comprises the degeneration and death of neurons, synapse loss, neuroinflammation and the intracellular as well as extracellular accumulation of proteins \cite{Koffie2011}. The protein amyloid-\textbeta\xspace (\Ab) is produced as part of the normal metabolism of healthy brains, but it plays a major role in the development of AD \cite{Haass1992}. According to the \Ab hypothesis AD is caused by a failure to remove \Ab from the brain and successively, its accumulation in the form of plaques in the parenchyma. Prior to the buildup of plaques in the brain \Ab accumulates in the walls of cerebral blood vessels as cerebral amyloid angiopathy (CAA), which correlates much better with the degree of dementia compared to the number and size of plaques and appears in \SIrange{90}{96}{\percent} of AD patients \cite{Weller2006, Weller2009}.

In order to process metabolites, the brain requires a lymphatic system that transports waste products to the lymph nodes, where they are decomposed. While the rest of the body possesses a dedicated network of lymphatic vessels these do not exist in the brain \cite{Weller2010}. Both the pathology of CAA and ample evidence from injection studies suggest that the basement membranes (BM) in the walls of cerebral arteries provide the clearance pathway for interstitial fluid (ISF) towards the surface of the brain, also referred to as intramural periarterial drainage (IPAD) \cite{Weller2010,Carare2008,Hawkes2011,Morris2014}. It is important not to confuse the IPAD pathway with the Virchow-Robin spaces, which are often referred to as perivascular (or ``paravascular'') spaces, possibly artefactual, located between the glia limitans and the arterial wall. Virchow-Robin spaces are virtual spaces and have no role in \Ab drainage. The BM forming the IPAD does not actually constitute a space, but rather a fluid-filled protein matrix. Our understanding of the mechanism that drives perivascular drainage through the BM is still very limited. The evidence indicates that ISF enters the BM at the capillary level and flows towards the lymph nodes in the neck via the BM cerebral arteries. This suggests that the counterintuitive phenomenon of ISF flow occurs in the reverse direction to blood flow \cite{Carare2008}.
